|

### 2020-05-21 paper/Manuscript.Rmd
Create escape option for literal double at

It is easiest to mark the distinction between essential and non-essential references from the start, instead of going
back to cut references prior to publication. Therefore, the `worcs` package distinguishes between the
traditional at-symbol (`@`) used to cite a reference, and the "double at"-symbol (`@@`), used to cite a non-essential reference.
Users can render a manuscript to PDF either with, or without, comprehensive citations.

@@

1. During writing, maintain a plain-text `.bib` file with the BibTeX references for all citations.
    + You can make this file by hand; e.g., Figure \@ref(fig:scholarbib) shows how to obtain a BibTeX reference from Google Scholar; simply copy-paste each reference into the `.bib` file
    + You can export a `.bib` file from most reference manager programs; the free, open-source reference manager [Zotero](https://www.zotero.org/download/) is excellent and user-friendly, and highly interoperable with other commercial reference managers. [Here](https://christopherjunk.netlify.com/blog/2019/02/25/zotero-rmarkdown/) is a tutorial for using Zotero with Rmarkdown.
2. To cite a reference, use the `citekey` - the first word in the BibTeX entry for that reference. Insert it in the Rmarkdown file like so: `@yourcitekey2020`. For a parenthesized reference, use `[@citekeyone2020; @citekeytwo2020]`. For more options, see the [Rmarkdown cookbook](https://bookdown.org/yihui/rmarkdown-cookbook/bibliography.html).
3. To indicate a *non-essential* citation, mark it with a double at-symbol: `@@nonessential2020`.
4. When Knitting the document, adapt the `knit` command in the YAML header.  
  `knit: worcs::cite_all` renders all citations, and  
  `knit: worcs::cite_essential` removes all *non-essential* citations.
5. Optional: To be extremely thorough, you could make a "branch" of the GitHub repository for the print version of the manuscript. Only in this branch, you use the function `knit: worcs::cite_essential`. The procedure is documented in [this tutorial](http://rstudio-pubs-static.s3.amazonaws.com/142364_3b344a38149b465c8ebc9a8cd2eee3aa.html).

>>>>

It is easiest to mark the distinction between essential and non-essential references from the start, instead of going
back to cut references prior to publication. Therefore, the `worcs` package distinguishes between the
traditional at-symbol (`@`) used to cite a reference, and the "double at"-symbol (`\@\@`), used to cite a non-essential reference.
Users can render a manuscript to PDF either with, or without, comprehensive citations.

@@

1. During writing, maintain a plain-text `.bib` file with the BibTeX references for all citations.
    + You can make this file by hand; e.g., Figure \@ref(fig:scholarbib) shows how to obtain a BibTeX reference from Google Scholar; simply copy-paste each reference into the `.bib` file
    + You can export a `.bib` file from most reference manager programs; the free, open-source reference manager [Zotero](https://www.zotero.org/download/) is excellent and user-friendly, and highly interoperable with other commercial reference managers. [Here](https://christopherjunk.netlify.com/blog/2019/02/25/zotero-rmarkdown/) is a tutorial for using Zotero with Rmarkdown.
2. To cite a reference, use the `citekey` - the first word in the BibTeX entry for that reference. Insert it in the Rmarkdown file like so: `@yourcitekey2020`. For a parenthesized reference, use `[@citekeyone2020; @citekeytwo2020]`. For more options, see the [Rmarkdown cookbook](https://bookdown.org/yihui/rmarkdown-cookbook/bibliography.html).
3. To indicate a *non-essential* citation, mark it with a double at-symbol: `\@\@nonessential2020`.
4. When Knitting the document, adapt the `knit` command in the YAML header.  
  `knit: worcs::cite_all` renders all citations, and  
  `knit: worcs::cite_essential` removes all *non-essential* citations.
5. Optional: To be extremely thorough, you could make a "branch" of the GitHub repository for the print version of the manuscript. Only in this branch, you use the function `knit: worcs::cite_essential`. The procedure is documented in [this tutorial](http://rstudio-pubs-static.s3.amazonaws.com/142364_3b344a38149b465c8ebc9a8cd2eee3aa.html).
